### 2012-04-10 doc/theses/mikula/conclusion.tex
Master thesis: Final corrections.

As the main advantages and disadvantages of the work we list the following.
\begin{itemize}
\renewcommand{\labelitemi}{$+$}
\item Elaboration of the overview how XQuery queries can help in the process of XML schema inference.
\item Incorporation of the lexical and syntax analyses of input queries creating their syntax trees.
\item Development of the static type analysis including PathTypes, which can be easily extended and use in possible future extensions.
\item Extension of the existing method of key discovery, achieving better results.
\item Our implementation using the jInfer framework is the first implementation of XML schema inference method utilizing XML operations.
\renewcommand{\labelitemi}{$-$}
\item In the proposed algorithm we dealt with a small part of possible refinements discussed in the overview.
\item The combination with existing methods of inference is done in the simplest way, not modifying the grammar rules. But, from the view of recent XML schema inference research, the modification of the grammar rules according to the statements inferred from XML operations is vastly interesting.
\item Since large real-world sets of XQuery queries are not available, we did not perform experiments using such sets. We only tested our method using a relatively small number input of queries, decreasing the level of reliability of the experimental results.
\end{itemize}

>>>>

As the main advantages and disadvantages of the work we list the following.
\begin{itemize}
\renewcommand{\labelitemi}{$+$}
\item Elaboration of the overview how XQuery queries can help in the process of XML schema inference.
\item Incorporation of the lexical and syntax analyses of input queries creating their syntax trees.
\item Development of the static type analysis including PathTypes, which can be easily extended and used in possible future extensions.
\item Extension of the existing method of key discovery, achieving better results.
\item Our implementation using the jInfer framework is the first implementation of XML schema inference method utilizing XML operations.
\renewcommand{\labelitemi}{$-$}
\item In the proposed algorithm we dealt with only a small part of possible refinements discussed in the overview. The reason for this is that inclusion of more of them would exceed scope of one thesis.
\item The combination with existing methods of inference is done in the simplest possible way - by not modifying the grammar rules. However, in the view of recent XML schema inference research, the modification of the grammar rules according to the statements inferred from XML operations is of considerable interest. The reason for the simplest combination is related with the previous point and it is that we did not deal with refinements affecting the grammar rules.
\item Since large real-world sets of XQuery queries are not available, we did not perform tests using such sets. We only tested our method using a relatively small number of input queries, decreasing the level of reliability of the experimental results.
\end{itemize}
